Case Study (McKenna)

### 2020-08-05 Cases/mrp/Case Study (McKenna) .Rmd
Started describing the models and identifying gaps in understanding that need to be addressed.

```{stan logit-hier, output.var="logit_hier", eval=FALSE}
data {
  int<lower=1> D;
  int<lower=0> N;
  int<lower=1> L;
  int<lower=0,upper=1> y[N];
  int<lower=1,upper=L> ll[N];
  matrix[N, D] x;
}

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```

@@

BEFORE FITTING downes_copy.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...

@@

  int<lower=0,upper=n_age> age[n];                  // These are the variables containing
  int<lower=0,upper=n_eth> eth[n];                        // the observed data for each
  int<lower=0,upper=n_income> income[n];                    // poststratification factor in the 
  int<lower=0,upper=n_male> male[n];                      // final model
  int<lower=0,upper=n_state> state[n];      
 }
parameters {                                            // Model parameters to be estimated:
  real b0;                                              // "intercept"
  real a_age[n_age];                                // age varying coeffs (depart from linear fit)
  real a_eth[n_eth];                                      // remoteness class varying coeffs 
  real a_income[n_income];                                    // seifa ieo varying coeffs (depart linear fit)
  real a_male[n_male];                                // english fluency varying coeffs
  real a_state[n_state];                                  // occupation varying coeffs
  real<lower=0> sigma_age;                            // age var(sd) component
  real<lower=0> sigma_eth;                               // remoteness class var(sd) component
  real<lower=0> sigma_income;                              // seifa ieo var(sd) component
  real<lower=0> sigma_male;                            // english fluency var(sd) component
  real<lower=0> sigma_state;                             // occupation var(sd) component
}
transformed parameters {                                // Model specification is here
  vector[n] outcome_hat;
  for (i in 1:n) {
    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
  }
}
model {                                                 // Model distributions for varying coefficients
  b0 ~ cauchy(0,2.5);                                   // and prior distributions for unmodelled                            // Can modify Cauchy scale parameter
                                                        // Can also specify a uniform distribution here
  a_age ~ normal(0, sigma_age);                     // or by setting upper and lower limits for
  a_eth ~ normal(0, sigma_eth);                           // unmodelled parameters in the parameter step
  a_income ~ normal(0, sigma_income);                         // above  
  a_male ~ normal(0, sigma_male);                      
  a_state ~ normal(0, sigma_state);

@@

BEFORE FITTING stan_mrp.stan INCLUDE IT HERE AND EXPLAIN THE MODEL...

>>>>

```{stan logit-hier, output.var="logit_hier", eval=FALSE}
data {
  int<lower=1> D;                // Number of variables.
  int<lower=0> N;                // Number of observations.
  int<lower=1> L;                // Number of groups.
  int<lower=0,upper=1> y[N];     // Outcome variable. 
  int<lower=1,upper=L> ll[N];    // Group assignment. 
  matrix[N, D] x;                // Matrix of predictors. 
}

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```
```{r, eval = FALSE}
posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)

?posterior_linpred

poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)

model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))

round(model_popn_pref, 3)
```

@@

The data section of the Downes model not only specifies the individual predictor values but also the number of categories for each categorical variable. Each category is given a varying coefficient in the parameter section.

[Note to McKenna]
Questions to answer: 
Why cauchy?
Actual model specification?
Why varying coefficients?

@@

  int<lower=0,upper=n_age> age[n];                    // These are the variables containing
  int<lower=0,upper=n_eth> eth[n];                    // the observed data for each
  int<lower=0,upper=n_income> income[n];              // poststratification factor in the 
  int<lower=0,upper=n_male> male[n];                  // final model
  int<lower=0,upper=n_state> state[n];      
 }
parameters {                                          // Model parameters to be estimated:
  real b0;                                            // "intercept"
  real a_age[n_age];                                  // age varying coeffs (depart from linear fit)
  real a_eth[n_eth];                                  // ethnicity class varying coeffs 
  real a_income[n_income];                            // income varying coeffs (depart linear fit)
  real a_male[n_male];                                // gender varying coeffs
  real a_state[n_state];                              // state varying coeffs
  real<lower=0> sigma_age;                            // age var(sd) component
  real<lower=0> sigma_eth;                            // ethnicit var(sd) component
  real<lower=0> sigma_income;                         // income var(sd) component
  real<lower=0> sigma_male;                           // gender fluency var(sd) component
  real<lower=0> sigma_state;                          // state var(sd) component
}
transformed parameters {                              // Model specification is here
  vector[n] outcome_hat;
  for (i in 1:n) {
    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
  }
}
model {                                              // Model distributions for varying coefficients
  b0 ~ cauchy(0,2.5);                                // and prior distributions for unmodelled                                                                // Can modify Cauchy scale parameter
                                                     // Can also specify a uniform distribution here
  a_age ~ normal(0, sigma_age);                      // or by setting upper and lower limits for
  a_eth ~ normal(0, sigma_eth);                      // unmodelled parameters in the parameter step
  a_income ~ normal(0, sigma_income);                // above  
  a_male ~ normal(0, sigma_male);                      
  a_state ~ normal(0, sigma_state);

@@

The data for the Stan User Guide model is specified with lower and upper bounds on the data for the number of categories for each variable. In this stan model, post-stratification takes place in the generated quantities section.

[Note to McKenna]
Questions to answer: 
What the epsilon, -epsilon is that?
